Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
Manual merge

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
\newcommand{\system}{\textsc{CoCoSea}~}
\newcommand{\systemEnding}{\textsc{CoCoSea}}
\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{"#1"}}}}

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1b9e77}
\definecolor{pop2}{HTML}{d95f02}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}

@@

\title{Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning}

@@

    \end{tabular}
    ~\\
    \midrule
    \rotatebox[origin=c]{90}{\normalsize DSL}&
    \hspace{0cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      $f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}\\
      \hspace{\helpSize}($f_1$: \emph{Append the number }\code{k}\emph{ to $\ell$})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      $f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\
      \phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      $f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
      \phantom{$f_1(\ell,$}
      \code{($\lambda$ (x a) (if a a (= k x))))}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}&

  \hspace{0.5cm}\begin{tabular}{l}
    $f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$ (x)}\\\hspace{1cm}\code{ (if (= x a) b x)) s)}\\
      \hspace{\helpSize}($f_0$: \emph{Performs character substitution)}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}\\
        \hspace{\helpSize}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car }\\\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}\\
        \hspace{\helpSize}($f_2$: \emph{Abbreviates a sequence of words})\\
        $f_3($\code{a}$,$\code{b}$) \,=\, $\code{(foldr a b cons)}\\
      \hspace{\helpSize}($f_3$: \emph{Concatenate strings }\code{a}\emph{ and }\code{b})
  \end{tabular}&

  \begin{tabular}{l}
    $f_0($\code{x}$)\,=\,$\code{(+ x real)}\\
    $f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} \\
    $f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}\\
    $f_3($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_2$\code{ x)))}\\
    $f_4($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_3$\code{ x)))}\\
    \hspace{\helpSize}\emph{($f_4$: 4th order polynomial)}\\
        $f_5($\code{x}$)\,=\,$\code{(/ real x)}\\
    $f_6($\code{x}$)\,=\,$\code{($f_4$ ($f_0$ x))} \\
    \hspace{\helpSize}\emph{($f_6$: rational function)}\\

@@

          \node(l1) at (0,0) {};
  \node[color=pop1](p1) at (-1,-1) {\code{+}};
  \node[color=pop1](n1) at (0.7,-0.9) {\code{1}};
  \node(x1) at (0,-1) {\code{1}};
  \draw[color=pop1] (l1.south) -- (p1.north);
  \draw[color=pop1] (l1.south) -- (n1.north);
  \draw[color=pop1] (-0.5,-0.5) -- (x1.north);

@@

  \begin{scope}[shift={(0,-2.5)}]
      \node(l1) at (0,0) {};
  \node[color=pop1](p1) at (-1,-1) {\code{+}};
  \node[color=pop1](n1) at (0.7,-0.9) {\code{1}};
  %\node(x1) at (0,-1) {};
  \draw[color=pop1] (l1.south) -- (p1.north);
  \draw[color=pop1] (l1.south) -- (n1.north);
  \draw[color=pop1] (-0.5,-0.5) -- (0,-1);

@@

\begin{scope}[shift={(0,-5)}]
  \node[pop1](p1) at (-1,-1) {\code{+}};
  \node[pop1](n1) at (0.8,-0.7) {\code{1}};
  \node[pop1](a) at (0,-1) {\code{ }};
  %\node(x1) at (0,-1) {};
  \draw[pop1] (0,0) -- (p1.north);
  \draw[pop1] (0,0) -- (n1.north);
  \draw[pop1] (-0.55,-0.4) -- (a.north);
  \node [rotate=90] at (-2.3,-0.7) {\small fragment};

@@

\section{Symbolic Regression: Programs from visual input}\label{regressionSection}
We apply \system
to symbolic regression problems.  Here, the
agent observes points along the curve of a function, and must write a
program that fits those points.  We initially equip our learner with
addition, multiplication, and division, and task it with solving
100 symbolic regression problems, each either a polynomial of degree
1--4 or a rational function.  The recognition model is a
convolutional network that observes an image of the target function's
graph (Fig.~\ref{functions}) -- visually, different kinds of
polynomials and rational functions produce different kinds of graphs,
and so the recognition model can learn to look at a graph and predict
what kind of function best explains it.  A key difficulty, however, is
that these problems are best solved with programs containing real
numbers.  Our solution to this difficulty is to allow the system to
write programs with real-valued parameters, and then fit those
parameters by automatically differentiating through the programs the
system writes and use gradient descent to fit the parameters.
We define the likelihood model, $\probability[x|p]$, by assuming a Gaussian noise model for the input/output examples,
and penalize the use of real-valued parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.

\begin{wrapfigure}{r}{0.45\textwidth}\vspace{-0.5cm} \newcommand{\functionSize}{1.5cm}\centering
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/48.png}
  \includegraphics[width = \functionSize]{figures/functions/102.png}
  \includegraphics[width = \functionSize]{figures/functions/116.png}\\
  \vspace{1pt}\includegraphics[width = \functionSize]{figures/functions/181.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/149.png}
    \includegraphics[width = \functionSize]{figures/functions/187.png}
  \caption{Recognition model input for symbolic regression. DSL learns subroutines for polynomials (top row) and polynomials (bottom row) while the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines best explains the observation.}\label{functions}\vspace{-2cm}
\end{wrapfigure}
\system learns a DSL containing 13 new functions,
most of which are templates for polynomials of different orders or ratios of polynomials.
It also learns to find programs that minimize the number of continuous degrees of freedom.
For example, it learns to represent linear functions with the program
\code{(* real (+ x real))}}, which has two continuous degrees of freedom, and represents quartic functions using the invented DSL primitive $f_4$ in the rightmost column of Fig.~\ref{initialExampleDSL}
which has five continuous parameters.
This phenomenon arises from our Bayesian framing -- both the implicit bias towards shorter programs and the likelihood model's BIC penalty.

@@

We compare with ablations of our model on held out tasks.
The purpose of this ablation study is 
both to examine the role of each component of \systemEnding,
as well as to compare with
prior approaches in the literature:
a head-to-head
comparison of program synthesizers is complicated by the fact that
each system, including ours, makes idiosyncratic 
assumptions about the space of programs and the statement of tasks.
\begin{wraptable}{r}{0.55\textwidth}
\vspace{-5pt}
%% This radically shrinks the table
\tabcolsep=2.5pt
\renewcommand{\arraystretch}{0.5}
\begin{tabular}{lcccccc}
  \toprule& Ours& 
    No NN & SE&NPS & PCFG & Enum \\
  \midrule
  \multicolumn{7}{c}{\emph{List Processing}}\\
  \midrule
  \% solved&\textbf{79\%} &76\% &71\%&35\%&62\%&37\%\\
  Solve time&  4.1s&5.8s&10.6s&34.7s&43.4s&20.2s\\
  \midrule
  \multicolumn{7}{c}{\emph{Text Editing}}\\
  \midrule
  \% solved&\textbf{74\%} &43\% &30\%&33\%&0\%&4\%\\
  Solve time& 29s&65s&38s&80s&--&235s\\
  \midrule
  \multicolumn{7}{c}{\emph{Symbolic Regression}}\\
  \midrule
  \% solved&   \textbf{84\% }&75\%&62\%&38\%&38\%&37\% \\
  Solve time&  24s& 40s  &28s&31s&55s&29s\\
  \bottomrule
  \end{tabular}
\caption{\% solved before timeout. Solve time: averaged over solved
  tasks.  SE: NPS: trained like RobustFill/DeepCoder.  PCFG: model w/o
  structure learning.  Enum: model w/o any learning.  %% MDL:
  %% $-\expect\left[\probability[x|p] \right]$. For domains other than
  %% symbolic regression MDL is 0 nats.
  %% For symbolic regression MDL is a
  %% proxy for \# of continuous parameters.
}\vspace{-0.5cm}\label{baselineComparisons} \end{wraptable}
Nevertheless, much prior work can be modeled within our setup. 
We compare with the following baselines:
\\\noindent \textbf{No NN}, which lesions the recognition model.
\\\noindent \textbf{NPS}, which does not learn the DSL,
instead learning the recognition model
from samples drawn from the fixed DSL.
We call this NPS (Neural Program Synthesis)
because this setup is closest to how
RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
\\\noindent \textbf{SE}, which lesions the recognition model and restricts the DSL  learning algorithm to
only add \textbf{s}ub\textbf{e}xpressions of programs in the frontiers to the DSL. This is how prior approaches have learned libraries of functions~\cite{Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,DBLP:conf/ecai/LinDETM14}.
\\\noindent \textbf{PCFG}, which lesions the recognition model and does not learn the DSL,
but instead learns the parameters of the DSL ($\theta$).
and is like learning the parameters of a PCFG while not learning any of the structure.
\\\noindent \textbf{Enum}, which enumerates a frontier without any learning -- equivalently, our first search step.

>>>>

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket #1 \rrbracket}

\newcommand{\system}{\textsc{SCC}~}
\newcommand{\systemEnding}{\textsc{SCC}}

\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{"#1"}}}}

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1f78b4}
\definecolor{pop2}{HTML}{33a02c}
\definecolor{pop3}{HTML}{d95f02}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}

@@

\title{Search, Compress, Compile: Library Learning in Neurally-Guided Bayesian Program Learning}

@@

    \end{tabular}
    ~\\
    \midrule
    \rotatebox[origin=c]{90}{\normalsize \popp{DSL}}&
    \hspace{0cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      \popp{$f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      \popp{$f_1(\ell,$\code{k}$) \,=\, $\code{($f_0$ (cons k nil) $\ell$)}}\\
      \hspace{\helpSize}($f_1$: \emph{Append the number }\code{k}\emph{ to $\ell$})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      \popp{$f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}}\\
      \popp{\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      \popp{$f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}}\\
      \phantom{$f_1(\ell,$}
      \popp{\code{($\lambda$ (x a) (if a a (= k x))))}}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}&

  \hspace{0.5cm}\begin{tabular}{l}
    \popp{$f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$
    (x)}}\\
    \popp{\hspace{1cm}\code{ (if (= x a) b x)) s)}}\\
      \hspace{\helpSize}($f_0$: \emph{Performs character substitution)}\\
      \popp{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x
      a)}\\\hspace{1.1cm}\code{ (cdr (if (= c x) s a))))}}\\
        \hspace{\helpSize}($f_1$: \emph{Drop characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      \popp{$f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car
      }}\\
      \popp{\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}}\\
        \hspace{\helpSize}($f_2$: \emph{Abbreviates a sequence of words})\\
        \popp{$f_3($\code{a}$,$\code{b}$) \,=\, $\code{(foldr a b cons)}}\\
      \hspace{\helpSize}($f_3$: \emph{Concatenate strings }\code{a}\emph{ and }\code{b})
  \end{tabular}&

  \begin{tabular}{l}
    \popp{$f_0($\code{x}$)\,=\,$\code{(+ x real)}}\\
    \popp{$f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} }\\
    \popp{$f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}}\\
    \popp{$f_3($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_2$\code{ x)))}}\\
    \popp{$f_4($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_3$\code{ x)))}}\\
    \hspace{\helpSize}\emph{($f_4$: 4th order polynomial)}\\
    \popp{$f_5($\code{x}$)\,=\,$\code{(/ real x)}}\\
    \popp{$f_6($\code{x}$)\,=\,$\code{($f_4$ ($f_0$ x))}}\\
    \hspace{\helpSize}\emph{($f_6$: rational function)}\\

@@

          \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  \node(x1) at (0,-1) {\code{1}};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (x1.north);

@@

  \begin{scope}[shift={(0,-2.5)}]
      \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  %\node(x1) at (0,-1) {};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

@@

\begin{scope}[shift={(0,-5)}]
  \node[pop3](p1) at (-1,-1) {\code{+}};
  \node[pop3](n1) at (0.8,-0.7) {\code{1}};
  \node[pop3](a) at (0,-1) {\code{ }};
  %\node(x1) at (0,-1) {};
  \draw[pop3] (0,0) -- (p1.north);
  \draw[pop3] (0,0) -- (n1.north);
  \draw[pop3] (-0.55,-0.4) -- (a.north);
  \node [rotate=90] at (-2.3,-0.7) {\small fragment};

@@

\section{Symbolic Regression: Programs from visual input}\label{regressionSection}
We apply \system
to symbolic regression problems.  Here, the
agent observes points along the curve of a function, and must write a
program that fits those points.  We initially equip our learner with
addition, multiplication, and division, and task it with solving
100 symbolic regression problems, each either a polynomial of degree
1--4 or a rational function.  The recognition model is a
convolutional network that observes an image of the target function's
graph (Fig.~\ref{functions}) -- visually, different kinds of
polynomials and rational functions produce different kinds of graphs,
and so the recognition model can learn to look at a graph and predict
what kind of function best explains it.  A key difficulty, however, is
that these problems are best solved with programs containing real
numbers.  Our solution to this difficulty is to enumerate
 programs with real-valued parameters, and then fit those
parameters by automatically differentiating through the programs the
system writes and use gradient descent to fit the parameters.
We define the likelihood model, $\probability[x|p]$, by assuming a Gaussian noise model for the input/output examples,
and penalize the use of real-valued parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.

\begin{wrapfigure}{r}{0.45\textwidth}\vspace{-0.5cm} \newcommand{\functionSize}{1.5cm}\centering
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/48.png}
  \includegraphics[width = \functionSize]{figures/functions/102.png}
  \includegraphics[width = \functionSize]{figures/functions/116.png}\\
  \vspace{1pt}\includegraphics[width = \functionSize]{figures/functions/181.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/149.png}
    \includegraphics[width = \functionSize]{figures/functions/187.png}
  \caption{Recognition model input for symbolic regression. DSL learns subroutines for polynomials (top row) and rational functions (bottom row) while the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines best explains the observation.}\label{functions}\vspace{-2cm}
\end{wrapfigure}
\system learns a DSL containing 13 new functions,
most of which are templates for polynomials of different orders or ratios of polynomials.
It also learns to find programs that minimize the number of continuous degrees of freedom.
For example, it learns to represent linear functions with the program
\code{(* real (+ x real))}, which has two continuous degrees of freedom, and represents quartic functions using the invented DSL primitive $f_4$ in the rightmost column of Fig.~\ref{initialExampleDSL}
which has five continuous parameters.
This phenomenon arises from our Bayesian framing -- both the implicit bias towards shorter programs and the likelihood model's BIC penalty.

@@

We compare with ablations of our model on held out tasks.
The purpose of this ablation study is 
both to examine the role of each component of \systemEnding,
as well as to compare with
prior approaches in the literature:
a head-to-head
comparison of program synthesizers is complicated by the fact that
each system, including ours, makes idiosyncratic 
assumptions about the space of programs and the statement of tasks.
\begin{wraptable}{r}{0.55\textwidth}
\vspace{-5pt}
%% This radically shrinks the table
\tabcolsep=2.5pt
\renewcommand{\arraystretch}{0.5}
\begin{tabular}{lcccccc}
  \toprule& Ours& 
    No NN & SE&NPS & PCFG & Enum \\
  \midrule
  \multicolumn{7}{c}{\emph{List Processing}}\\
  \midrule
  \% solved&\textbf{79\%}\footnote{A last-minute bug caused this  to run without ``Helmholtz machine'' style training ($\mathcal{L}_{\text{RM}} = \mathcal{L}_{\text{SS}}$). We are rerunning this experiment and expect this number to be higher.} &
  76\% &71\%&35\%&62\%&37\%\\
  Solve time&  4.1s&5.8s&10.6s&34.7s&43.4s&20.2s\\
  \midrule
  \multicolumn{7}{c}{\emph{Text Editing}}\\
  \midrule
  \% solved&\textbf{74\%} &43\% &30\%&33\%&0\%&4\%\\
  Solve time& 29s&65s&38s&80s&--&235s\\
  \midrule
  \multicolumn{7}{c}{\emph{Symbolic Regression}}\\
  \midrule
  \% solved&   \textbf{84\% }&75\%&62\%&38\%&38\%&37\% \\
  Solve time&  24s& 40s  &28s&31s&55s&29s\\
  \bottomrule
  \end{tabular}
\caption{\% solved before timeout. Solve time: averaged over solved
  tasks.  %SE: NPS: trained like RobustFill/DeepCoder.  PCFG: model w/o
  %structure learning.  Enum: model w/o any learning.  %% MDL:
  %% $-\expect\left[\probability[x|p] \right]$. For domains other than
  %% symbolic regression MDL is 0 nats.
  %% For symbolic regression MDL is a
  %% proxy for \# of continuous parameters.
}\vspace{-0.5cm}\label{baselineComparisons} \end{wraptable}
Nevertheless, much prior work can be modeled within our setup. 
We compare with the following ablations (Table~\ref{baselineComparisons}):
\\\noindent \textbf{No NN:} lesions the recognition model.
\\\noindent \textbf{NPS}, which does not learn the DSL,
instead learning the recognition model
from samples drawn from the fixed DSL.
We call this NPS (Neural Program Synthesis)
because this is closest to how
RobustFill~\cite{devlin2017robustfill} and DeepCoder~\cite{balog2016deepcoder} are trained.
\\\noindent \textbf{SE}, which lesions the recognition model and restricts the DSL  learning algorithm to
only add \textbf{s}ub\textbf{e}xpressions of programs in the frontiers to the DSL. This is how prior approaches have learned libraries of functions~\cite{Dechter:2013:BLV:2540128.2540316,DBLP:conf/icml/LiangJK10,DBLP:conf/ecai/LinDETM14}.
\\\noindent \textbf{PCFG}, which lesions the recognition model and does not learn the DSL,
but instead learns the parameters of the DSL ($\theta$) -- learning the parameters of a PCFG while not learning any of the structure.
\\\noindent \textbf{Enum}, which enumerates a frontier without any learning -- equivalently, our first search step.
